Output Summary

### 2020-10-27 03-post-process/output-plots.Rmd

`r if (params$mcmc_plots) "### $$\\sigma$"`

@@

@@

```{r}
# function to calculate posterior 
get_SAR_post = function(post, jags_data) {
  # extract posterior abundances
  Ra_post = post_subset(post, "^Ra[", T) # adults returning to tributary
  Mb_post = post_subset(post, "^Mb[", T) # smolts leaving tributary in spring

@@

@@

>>>>

`r if (params$mcmc_plots) "### $\\sigma$"`

@@

`r if (params$mcmc_plots) "### stray"`

_There are some elements of both `n_stray_tot` and `stray_comp` that are exactly zero each MCMC iteration. These are omitted from the plots below._

```{r stray-diag-plots, eval = params$mcmc_plots, fig.width = 7, fig.height = 7}
stray = post_subset(post, "stray", T)
non_zero_stray = apply(stray, 2, function(x) all(x != 0))
stray_nodes = names(non_zero_stray)[non_zero_stray]
diag_plots(post, stray_nodes, layout = "5x3")
```

@@

```{r sar-plot}
# function to calculate posterior 
get_SAR_post = function(post, jags_data) {
  # extract posterior abundances
  Ra_post = post_subset(post, "^Ra[", T) # adults returning to tributary
  Mb_post = post_subset(post, "^Mb[", T) # smolts leaving tributary in spring

@@

SAR_mean[SAR_mean == "Inf"] = NA
SAR_lwr[SAR_lwr == "Inf"] = NA
SAR_upr[SAR_upr == "Inf"] = NA

@@

# Number of Strays

```{r stray-tot-plot}
par(oma = c(1,1,0,0))
plot_tseries(post_summ(post, "n_stray_tot"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]))
mtext(side = 1, outer = T, line = -0.5, "Return Year")
mtext(side = 2, outer = T, line = 0, "Number of Strays")
```
